YouPower -- A Social App for User Engagement in Power Grids

### 2015-12-16 SCITEPRESS_Conference_Latex/relatedWork.tex
edited and improved parts of SotA.

\noindent Prior to designing YouPower, we review the existing studies with social smart grid platforms and summarize the lessons learned from those studies. We combine such lessons with the findings from the literature on pro-environmental behavior change and compile a set of design guidelines with successful strategies and potential barriers for social energy platforms. For instance, a repeatedly reported issue with such platforms is a lack of long term user engagement \cite{edward2015review}. We adopt iterative, open and lean co-design process \cite{folstad2008living,klein2013ux,leffingwell2010agile} that is suggested as a promising approach to avoid this issue \cite{schwartz2014people}.

@@

\paragraph{Design ideas and guidelines.} The literature review suggests that the most successful behavior change interventions combine several different strategies \cite{gardner1996environmental,ockwell2009reorienting}. However, a special care must be taken to avoid mixed messages \cite{knowles2014patterns}, especially when combining intrinsic and extrinsic motivations \cite{delmas2013information}.
Most of the solutions involve some type of \textit{consumption feedback}, such as historical or real-time (individual or group). Introduction of desrciptive or injunctive \textit{social norms} through comparative feedback, especially to the similar users, has proven effective \cite{allcott2011social,cialdini2001harnessing,petkov2011motivating}. Additionally, Strengers \cite{strengers2011designing} suggests combining feedback with \textit{practical recommendations (tips)} that lead to new practices which challenge taken-for-granted notions of normality. Several studies \cite{abrahamse2005review,delmas2013information} report tailored energy advice to a specific household and personalized information to be the most effective strategy. Another effective strategy that applies social dimension is \textit{public commitment} \cite{abrahamse2005review}, a procedure in which people are binding to a certain behavior. One suggestion to increase the effectiveness is to \textit{target organisations, companies and policy makers} \cite{hasselqvist2015supporting,brynjarsdottir2012sustainably} in addition to individuals.
Next, we describe how each of the strategies above is incorporated into the design of YouPower (for the full set of our design guidelines, refer to CIVIS D3.2.).

X Considering the analytical frames and the CIVIS use cases, we chose a set of platform features and translated those into three self-contained and composable parts to be included in the CIVIS (front-end) application (hereinafter abbreviated as CIVIS app): 
%\begin{enumerate}
%\item \nameref{sect:tips}
%\item \nameref{sect:brf}
%\item \nameref{sect:load_shifting}
%\end{enumerate}

>>>>

\noindent Prior to designing YouPower, we review the existing studies with social smart grid platforms and summarize the lessons learned from those studies. Combining such lessons with findings from the literature on pro-environmental behavior change we compile a set of design guidelines with successful strategies and potential barriers for social energy platforms. For instance, a repeatedly reported issue with such platforms is a lack of long term user engagement \cite{edward2015review}. We adopt iterative, open and lean co-design process \cite{folstad2008living,klein2013ux} that is suggested as a promising approach to avoid this issue \cite{schwartz2014people}.

@@

\paragraph{Design ideas and guidelines.} The literature review suggests that the most successful behavior change interventions combine several different strategies \cite{gardner1996environmental,ockwell2009reorienting}. However, a special care must be taken to avoid mixed messages \cite{knowles2014patterns}, especially when combining intrinsic and extrinsic motivations \cite{delmas2013information}. Additionally, the literature agrees that there is no a silver-bullet type of a solution and that we need interventions carefully \textit{attending to the context} \cite{hargreaves2013keeping,dillahunt2014understanding}.

Most of the solutions involve some type of \textit{consumption feedback}, such as historical or real-time (individual or group). Introduction of descriptive or injunctive \textit{social norms} through comparative feedback has proven effective \cite{allcott2011social,cialdini2001harnessing,petkov2011motivating}. Additionally, Strengers \cite{strengers2011designing} suggests combining feedback with \textit{practical recommendations (tips)} that lead to new practices which challenge taken-for-granted notions of normality. Several studies \cite{abrahamse2005review,delmas2013information} report tailored energy advice to a specific household and personalized information to be the most effective strategy. Another effective strategy that applies social dimension is \textit{public commitment} \cite{abrahamse2005review}, a procedure in which people are binding to a certain behavior. One suggestion to increase the effectiveness is to \textit{target organisations, companies and policy makers} \cite{hasselqvist2015supporting,brynjarsdottir2012sustainably} in addition to individuals.
Next, we describe how each of the strategies above is incorporated into the design of YouPower (for the full set of our design guidelines, refer to CIVIS D3.2.).

X Considering the recommendation to attend to the intervention context and the analytical frames above, we chose a set of platform features and translated those into three self-contained and composable parts so that each part will support different CIVIS use-cases and the specific socio-economic contexts in Stockholm and Trentino. The three parts included in the CIVIS (front-end) application (hereinafter abbreviated as CIVIS app) are: 
%\begin{enumerate}
%\item \nameref{sect:tips}
%\item \nameref{sect:brf}
%\item \nameref{sect:load_shifting}
%\end{enumerate}
